---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sameplot

<!-- badges: start -->
[![R-CMD-check](https://github.com/TomNaber/sameplot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/TomNaber/sameplot/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->
  
Render plots consistently across interactive R sessions, saved files, and knitr output by
drawing to a `ragg` device and displaying the resulting image via `knitr::include_graphics()`.

## Why?

RStudio’s plot pane, saved figures, and knitted documents can differ due to device and
rendering differences. `sameplot()` standardizes output by always rendering the plot to an
image first and then displaying *that* image.

## Installation

You can install the development version from GitHub:

```{r, eval = FALSE}
install.packages("pak")
pak::pak("TomNaber/sameplot")
```

Alternatively (remotes):

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("TomNaber/sameplot")
```

## Usage

```{r}
suppressPackageStartupMessages(library(sameplot))
suppressPackageStartupMessages(library(ggplot2))

p <- ggplot(mtcars, aes(wt, mpg)) +
  geom_point() +
  theme_minimal()

# 1) Display via a temporary PNG (useful in RStudio and when knitting)
sameplot(p)

# Using a temporary folder as example
tmp <- file.path(tempdir(), "sameplot-readme")

# 2) Save a PNG (to tempdir)
sameplot(p, file = file.path(tmp, "mtcars.png"), save = TRUE)

# 3) Save a TIFF (to tempdir; still displays via a temp PNG for compatibility)
sameplot(p, file = file.path(tmp, "mtcars.tiff"), save = TRUE)
```

## Notes

- Supported output extensions for saving: `.png`, `.tif`, `.tiff`.
- When `save = FALSE`, figures are written to a temporary location and cleaned up when
  the R session ends.
- `dpi` in the knitr output is set to the same value as `res` used for the `ragg` device.
